\RequirePackage[english=UKenglish]{hyphsubst}
\RequirePackage{acro}
\documentclass[twoside,openright,titlepage,numbers=noenddot,headinclude,footinclude=true,cleardoublepage=empty,listof=totoc,paper=a4,fontsize=12pt,australian,twoside=semi,DIV=calc]{scrreprt} 
% -----------------------------------------------------------------------------
%   CONFIGURATION
% -----------------------------------------------------------------------------
% Thesis and submission:
\newcommand{\myTitle}{Multi-scale modelling approaches to plasmon enhanced photo-catalysis on metallic nanoparticles}
\newcommand{\mySubmissionYear}{2022}
\newcommand{\mySubmissionMonth}{November}
\newcommand{\mySubmissionDay}{30}

% Regarding yourself:
\newcommand{\myFirstName}{Robert Michael}
\newcommand{\myLastName}{Jones}
\newcommand{\myWebsite}{https://www.kcl.ac.uk/people/robert-jones}
\newcommand{\myBirthYear}{1995}
\newcommand{\myBirthMonth}{November}
\newcommand{\myBirthDay}{02}
\newcommand{\myBirthPlace}{Stoke on Trent}

% Primary supervisor:
\newcommand{\myProfTitle}{Dr}
\newcommand{\myProfFirstName}{Francsca}
\newcommand{\myProfLastName}{Baletto}
\newcommand{\myProfWebsite}{https://www.unimi.it/en/ugov/person/francesca-baletto}

% Co-supervisor:
\newcommand{\mySecondProfTitle}{Professor}
\newcommand{\mySecondProfFirstName}{Anatoly}
\newcommand{\mySecondProfLastName}{Zayats}
\newcommand{\mySecondProfWebsite}{https://www.kcl.ac.uk/people/anatoly-zayats}

% Co-supervisor:
\newcommand{\myThirdProfTitle}{Dr}
\newcommand{\myThirdProfFirstName}{Roberto}
\newcommand{\myThirdProfLastName}{D'Agosta}
\newcommand{\myThirdProfWebsite}{http://nano-bio.ehu.es/users/dagosta}

% University related:
\newcommand{\TSCM}{Theory and Simulation of Condensed Matter}
\newcommand{\TSCMWebsite}{https://www.kcl.ac.uk/research/theory-simulation-of-condensed-matter}
\newcommand{\PNWebsite}{https://www.kcl.ac.uk/research/photonics-nanotechnology}
\newcommand{\PN}{Photonics \& Nanotechnology}
\newcommand{\myFaculty}{Faculty of Natural, Mathematical, \& Engineering Sciences}
\newcommand{\mySchool}{Department of Physics}
\newcommand{\myUni}{King's College London}
% -----------------------------------------------------------------------------

\input{classicthesis-config}
\usepackage[a4paper,top=25.4mm,bottom=25.4mm,left=25mm, right=25mm,bindingoffset=8mm]{geometry} 

\usepackage[acronym]{glossaries}
%\glsdisablehyper
%\makeglossaries
 
%\makeglossaries

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
%\input{text/ch0/ch0-gloss}
\usepackage{biblatex}
\addbibresource{Lib.bib}
\begin{document}
  \frenchspacing
  \raggedbottom
  \selectlanguage{british}
  \renewcommand*{\thefootnote}{\fnsymbol{footnote}}
  \pagestyle{plain}
  \pagenumbering{roman}
 
  \singlespacing
  \input{text/ch0/ch0-title}
  \input{text/ch0/ch0-backside}
  
  \onehalfspacing
  \input{text/ch0/ch0-contents}

%----------------------------------------------------------------------------------------
%	QUOTATION PAGE
%----------------------------------------------------------------------------------------

\vspace*{0.2\textheight}

\noindent\enquote{\itshape Who am I? Why am I here?
Forget the questions, someone get me another beer.
What's the meaning of life? What's the meaning of it all?
You gotta learn to dance before you learn to crawl.}\bigbreak

\hfill Meat Loaf

\vspace*{0.2\textheight}

\noindent\enquote{\itshape Fur immer Punk, das mocht' ich sein fur immer Punk. Willst du wirklich immer Hippie bleiben?}\bigbreak

\hfill Hladno Pivo

\vspace*{0.2\textheight}

\noindent\enquote{\itshape Lasciate ogne speranza, voi ch'intrate.}\bigbreak

\hfill Dante Alighieri

  \input{text/ch0/ch0-gloss}

  \chapter*{Abstract}
  \addcontentsline{toc}{chapter}{Abstract}
  \input{text/ch0/ch0-abstract}
  
  \chapter*{Statement of Authorship}
  \addcontentsline{toc}{chapter}{Declaration of Authorship}
  \input{text/ch0/ch0-declaration}
  
  \input{text/ch0/ch0-acknowledgements}
  \input{text/ch0/ch0-publications}
  \input{text/ch0/ch0-dedication}
%

  \cleardoublepage
  \pagestyle{scrheadings}
  \pagenumbering{arabic}
  \onehalfspacing
  
  \chapter{Introduction}\label{c:Introduction}
  \input{text/Chapters/Intro}
  
  \chapter{Theory and background}\label{c:Theory}
  \input{text/Chapters/Theory}
  
    \chapter{Methods}\label{c:Methods}
  \input{text/Chapters/Methods}
  
  \chapter{Sapphire}\label{c:Sapphire}
  \input{text/Chapters/Sapphire}
  
  \chapter{Optical and electrostatic properties of Au-based nanoparticles}\label{c:L-M}
  \input{text/Chapters/DFT}  

  \chapter{Formation process of AuPt nanoalloys}\label{c:Coal}
  \input{text/Chapters/MD}

  \chapter{Alloying of plasmonic and catalytic metals}\label{c:Alloy}
  \input{text/Chapters/Metallics} 
 
    \chapter{AuPt in an environment}\label{c:Water}
  \input{text/Chapters/Water}
  
  \chapter{Conclusions}\label{c:Conclusions}
  \input{text/Chapters/Conclusions}

  \input{text/app-bibliography}
  
\end{document}  