\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

As is true with any grand adventure, this piece of work is not mine alone in the sense that many wonderful, inspiring, and wonderfully inspiring people have come into and often left my life at some point throughout my scientific escapade. There are many teachers and mentors who have left indelible imprints on who I am now - be it the wonder with which I see the world or the stubbornness with which I view authority. 
%
My first and most significant acknowledgement has to be to my mother, Mary Jones, who has never done anything but her best to equip me for a dynamical world by teaching me humility, to take risks, and the value of hard graft. I would like to thank my brother, Peter, who has been one of the best friends I could have asked for - always providing me with a place of safety or a whiskey when necessary. My sister, Evelyn, who has always challenged me to be better, and to reach higher through her own gleaming example. 
%
I cannot name all of them, but the friends I have made along my physics journey: Steven Laughton, Christa Brown, Adele Parry, Balkar Brier, Ginger Matt, Jozsef Mak, Hovan Lee, Martina Ruffino, and countless others! I thank you all for our many inspiring small-hours conversations, questionable adventures, and for being genuinely good people. 
%
A PhD cannot be written alone - and indeed an exceptional supervisor is necessary to help mould a student into a scientist. I have been beyond fortunate to have not one - but three incredible supervisors. Roberto; for your uncompromisingly brilliant mind, mathematical intuition, and refreshing sense of humour I cannot thank you enough. Anatoly; your patience and ability to always find time for science, your genuinely frightening efficiency and organisation, and your brilliant and inspired ideas have set for me an example which I wish to learn from and emulate. Finally, Francesca. You rescued my project at a time when it was not clear if I would even be able to continue. And through all of the disruptions that any professional relationship has had to endure, you have always been a shining example of how a supervisor ought to guide their student. So thank you, Francesca. 
%
And thank you everyone who has participated in my journey in any capacity. Know that even if you are not explicitly named - you are considered and thanked for your own contribution to this project.